---
title: "hw10 R_slides"
author: "YI-Hsuan Lo"
output: 
  html_document:
    toc: true
    theme: united
---
##1. general calculating

Operator|	Description 
-|-
+|	Addition  
¡V|	Subtraction  
*|	Multiplication  
/|	Division  
^|	Exponent  
%%|	Modulus (Remainder from division)  
%/%|	Integer Division

```{r}
20*3
```
Operator| Description
-|-
>| bigger than
<| smaller than
>=| bigger than or equal to
<=| smaller then or equal to
==| equal to
!=| not equal to

```{r}
8>=9
```

##2. Data Types
###`vector`

```{r}
a <- c(1,2,5.3,6,-2,4) # numeric vector
b <- c("one","two","three") # character vector
c <- c(TRUE,TRUE,TRUE,FALSE,TRUE,FALSE) #logical vector
d <- a[c(2,4)] # 2nd and 4th elements of vector
```
```{r}
print(a)
print(b)
print(c)
print(d)
```
###`matrix`

```{r}
# generates 5 x 4 numeric matrix 
x=matrix(1:20, nrow=5,ncol=4)
print(x)
```
$$x=
\left[
\begin{matrix}
   1 & 6 & 11 & 16 \\
   2 & 7 & 12 & 17 \\
   3 & 8 & 13 & 18 \\
   4 & 9 & 14 & 19 \\
   5 & 10 & 15 & 20 \\
  \end{matrix} 
\right]$$
```{r}
x[,4] # 4th column of matrix
x[3,] # 3rd row of matrix 
x[2:4,1:3] # rows 2,3,4 of columns 1,2,3
```

###`array`
```{r}
array(1:24, dim = c(4, 3, 2))
```

###`factor`
```{r}
food <- c("cake", "cookie", "fish", "cake", "fish") 
food <- factor(food)
food 
```
```{r}
levels(food)
```

###`data frame`
```{r}
d <- c(1,2,3,4)
e <- c("red", "white", "red", NA)
f <- c(TRUE,TRUE,TRUE,FALSE)
mydata <- data.frame(d,e,f)
names(mydata) <- c("ID","Color","Passed") # variable names
```
```{r}
print(mydata)
```

###`list`
```{r}
student <- list(gender="woman", age=15)
student 
```
```{r}
str(student)
```


##3. Functions
###`if() statements`

>if (test_expression) {
statement
}

```{r}
x <- 5
if(x > 0){
print("Positive number")
}
```

>if (test_expression) {
statement1
} else {
statement2
}

```{r}
x <- -5
if(x > 0){
print("Non-negative number")
} else {
print("Negative number")
}
```
```{r}
if(x > 0) print("Non-negative number") else print("Negative number")
```

>if ( test_expression1) {
statement1
} else if ( test_expression2) {
statement2
} else if ( test_expression3) {
statement3
} else {
statement4
}

```{r}
x <- 0
if (x < 0) {
print("Negative number")
} else if (x > 0) {
print("Positive number")
} else
print("Zero")
```

###`for() loops`

> for (val in sequence)
> {
> statement
> }

```{r}
x <- c(2,5,3,9,8,11,6)
count <- 0
for (val in x) {
if(val %% 2 == 0)  count = count+1
}
print(count)
```

###`wile() loops`

> while (test_expression)
> {
> statement
> }

```{r}
i <- 1
while (i < 6) {
print(i)
i = i+1
}
```

###`repeat loop` and `break``next`

`repeat loop`

>repeat {
statement
}

```{r}
x <- 1
repeat {
print(x)
x = x+1
if (x == 6){
break
}
}
```

`break`
>if (test_expression) {
break
}

```{r}
x <- 1:5
for (val in x) {
if (val == 3){
break
}
print(val)
}
```

`next`

>if (test_condition) {
next
}

```{r}
x <- 1:5
for (val in x) {
if (val == 3){
next
}
print(val)
}
```

### useful functions
```{r}
object='hello'

length(object) # number of elements or components
str(object)    # structure of an object 
class(object)  # class or type of an object
names(object)  # names

c(object,object)       # combine objects into a vector
cbind(object, object) # combine objects as columns
rbind(object, object) # combine objects as rows 

object     # prints the object

ls()       # list current objects
rm(object) # delete an object

fix(object)               # edit in place
```

##4. Graphics
### `bar charts` 
```{r}
barplot(VADeaths, beside=TRUE, legend=TRUE, ylim=c(0, 90),
ylab="Deaths per 1000",
main="Death rates in Virginia")
```

### `dot charts`
```{r}
dotchart(VADeaths, xlim=c(0, 75),
 xlab="Deaths per 1000",
 main="Death rates in Virginia")
```

### `pie charts`
```{r}
groupsizes <- c(18, 30, 32, 10, 10)
labels <- c("A", "B", "C", "D", "F")
pie(groupsizes, labels, col=c("grey40", "white", "grey", "black", "grey90"))
```

### `histograms`
```{r}
x <- rnorm(100)
 hist(x)
```

### `box plots`
```{r}
boxplot(Sepal.Length~Species, data = iris,ylab = "Sepal length (cm)", main = "Iris measurements",
boxwex = 0.5)
```

### `scatter plots`
```{r}
x <- rnorm(100) # assigns 100 random normal observations to x
y <- rpois(100, 30) # assigns 100 random Poisson observations
# to y; mean value is 30
mean(y)

plot(x, y, main = "Poisson versus Normal")
plot(x, y, type="l") # plots a broken line (a dense tangle of line segments here)
plot(sort(x), sort(y), type="l") # a plot of the sample "quantiles"
```

### `QQ plots`
```{r}
X <- rnorm(1000)
A <- rnorm(1000)
qqplot(X, A, main="A and X are the same")
B <- rnorm(1000, mean=3, sd=2)
qqplot(X, B, main="B is rescaled X")
C <- rt(1000, df=2)
qqplot(X, C, main="C has heavier tails")
D <- exp(rnorm(1000))
qqplot(X, D, main="D is skewed to the right")
```

##5. Simulations
### `Uniform`

>ƒÜ	runif(n,min=a,max=b) default: a=0,b=1,n=ÀH¾÷ªºn­Ó¼Æ

```{r}
runif(10) #ÀH¾÷¨ú¤Q­Ó¼Æ
```

### `Bernoulli`

only two possible outcomes.
```{r}
set.seed(23207) # use this to obtain our output
guesses <- runif(20)
correct.answers <- (guesses < 0.2)
correct.answers

table(correct.answers)
```

### `Binomial`
```{r}
dbinom(x = 4, size = 6, prob = 0.5)
pbinom(4,6,0.5)
qbinom(0.89,6,0.5)
rbinom(24,15,0.1)
```

### `Poission`
```{r}
dpois(x = 3, lambda = 0.5)
ppois(3,0.5)
qpois(0.03,0.5)
rpois(10, 3.7)
```

### `Exponential`
```{r}
pexp(1, rate = 3)
rexp(10, rate = 3)

```

### `Normal`
```{r}
qnorm(0.95, mean = 2.7, sd = 3.3)
rnorm(10, -3, 0.5)

x<- rnorm(100000) # simulate from the standard normal
x <- x[(0 < x) & (x < 3)] # reject all x¡¦s outside (0,3)
hist(x, probability=TRUE) # show the simulated values
```

##6. Linear Programming
```{r,echo=F,warning=F}
library(lpSolve)
```
$$minC =5x_1 +8x_2$$  
$$x_1 +x_2 \geq 2$$
$$x_1 +2x_2 \geq 3$$
$$x_1,x_2 \geq 0$$
```{r}
eg.lp <- lp(objective.in=c(5, 8), const.mat=matrix(c(1, 1, 1, 2),  nrow=2), const.rhs=c(2, 3), const.dir=c(">=", ">="))
eg.lp
x1x2=eg.lp$solution 
```
(x1,x2)=(`r x1x2`)  
$$minC =5x_1 +8x_2=13$$  






